State of the Practice for Medical Imaging Software

### 2022-10-14 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP_AcademicRadiology.tex
Added a link to the technology hurdles pain point

Section~\ref{painpoints} lists the advantages and disadvantages between native
and web applications. Here we give further suggestions to help with deciding
whether to adopt a web application.  The decision will be based on whether, on
balance, the web application improves the four factors identified by developers:
compatibility, maintainability, performance, and security. To enable
decision-making, a team will need to prioritize between these factors, based on
the team's objectives and experience. The suggestions are intended to provide
ideas and avenues for exploration; a web application might not be the right fit
for all projects and all teams.

@@

As described in Section~\ref{painpoints}, it is difficult for software
development teams to access real-world medical imaging datasets. This problem
restricts their capability and flexibility for testing. We provide some
suggestions as follows:

>>>>

Section~\ref{painpoints} describes technology hurdles
(\ppref{P_TechnologyHurdles}) that motivate considering the use of web
applications. Here we give further advice to help with deciding whether to adopt
a web application. The decision will be based on whether, on balance, the web
application improves the four factors identified by developers: compatibility,
maintainability, performance, and security. To enable decision-making, a team
will need to prioritize between these factors, based on the team's objectives
and experience. The suggestions are intended to provide ideas and avenues for
exploration; a web application might not be the right fit for all projects and
all teams.

@@

As described in Section~\ref{painpoints} technology hurdles
(\ppref{P_TechnologyHurdles}) make it difficult for software development teams
to access real-world medical imaging datasets. This problem restricts their
capability and flexibility for testing. We provide some suggestions as follows:
